---
title: "Regression Models Course Project"
author: "Muralidhar Areti"
date: "August 21, 2015"
output: pdf_document
---

# Executive Summary
This report utilises the `mtcars` dataset to explore the the impact of various variables on the quarter mile time of a car. The `mtcars` dataset was extracted from the 1974 _Motor Trend_ US magazine providing data based on 10 variables representing properties of car design and performance for 32 cars. Exploratory data analysis is used to understand at a glance the effects of number of cylinders, horsepower and weight have on performance (lower quarter mile times are better) and efficiency (higher miles per gallon are better). 

# Exploratory Data Analysis
Initial exploratory data analysis was used to ensure we had a good understanding of our dataset. The main packages loaded are the `dplyr` and `ggplot2` to assist us with processing and charting the data. 

```{r, echo=FALSE, results='hide'}
suppressPackageStartupMessages(library(dplyr))
library(ggplot2)
suppressPackageStartupMessages(library(GGally))
library(tidyr)
data(mtcars)
```

The first step of the exploratory data analysis is to preview the data present. Normally we would also look for the dimensions and summary, but those details are given from the `mtcars` dataset itself (in `R` you can run the `?mtcars` command for more details on the data set). 
```{r}
head(mtcars)
```

A summary of the results from the exploratory analysis (see Appendix) is provided below: 

Property | Performance (qsec) | Efficiency (mpg)
-------|-----|-----
More cylinders | Good | Bad
More horsepower | Good | Bad
More Weight | - | Bad

# Statistical Inference
From the exploratory analysis, we make the following null hypothesis for our statistical inference: Best performance can be obtained by providing more horsepower. We can use a T-test to obtain the p-value which dictate whether or not we reject our null hypothesis. 

```{r}
result = t.test(mtcars$hp, mtcars$qsec)
result$p.value
result$estimate
```

# Regression Analysis
```{r, results='hide'}
full_model = lm(qsec ~ ., data = mtcars)
summary(full_model)
```

The code above gives a residual standard error of 0.7685 on 21 degrees of freedom with an adjusted R-squared of 0.815. This tells us the model can explain for about 82% of variance in the performance.

```{r, results='hide'}
step_model = step(full_model, k=log(nrow(mtcars)))
summary(step_model)
```

The model selected is `qsec ~ disp + wt + vs + carb` with a residual standard error of 0.7588 on 27 degrees of freedom, an adjusted r-squared value of 0.8197 telling us that 82% of the variance of the performance. 

```{r, results='hide'}
dispWtVsCarb_model = lm(qsec ~ disp + wt + vs + carb, data=mtcars)
summary(dispWtVsCarb_model)
```

# Residual Analysis and Diagnosis
See Appendix for the residual plots. From the plots we can verify the following assumptions: 

1. The residuals vs fitted plot shows a consistent pattern
2. The normal Q-Q plot show the residuals are normally distributed (this is verified from the points being close to the line)
3. The Scale-Location plot confirms a constant variance assumption (because points are randomly distributed)
4. The residuals vs. leverage shows that we have no outliers as every data point falls within the 0.5 bands. 

# Conclusion
From the above analyses we can conclude that our basic assumptions of linear regression have been met. 

\pagebreak  

# Appendix

```{r, fig.height=3.25}
# figure 
ggplot(mtcars, aes(factor(cyl), qsec)) + 
    geom_boxplot() + 
    geom_point(aes(colour=cyl)) +
    theme_bw()

# figure 
ggplot(mtcars, aes(factor(cyl), mpg)) + 
    geom_boxplot() + 
    geom_point(aes(colour=cyl)) +
    theme_bw()
```


<!--
```{r, fig.height=3.5}
# figure 
ggplot(mtcars, aes(disp, qsec)) + 
    geom_point(aes(colour=cyl)) + 
    theme_bw()

# figure 
ggplot(mtcars, aes(disp, mpg)) + 
    geom_point(aes(colour=cyl)) + 
    theme_bw()
```
--> 

\pagebreak

```{r, fig.height=3.5}
# figure 
ggplot(mtcars, aes(hp, qsec)) + 
    geom_point(aes(colour=cyl)) + 
    theme_bw()

# figure 
ggplot(mtcars, aes(hp, mpg)) + 
    geom_point(aes(colour=cyl)) + 
    theme_bw()
```

\pagebreak 

```{r, fig.height=3.5}
# figure 
ggplot(mtcars, aes(wt, qsec)) + 
    geom_point() + 
    theme_bw()

# figure 
ggplot(mtcars, aes(wt, mpg)) + 
    geom_point() + 
    theme_bw()
```

\pagebreak  

```{r, fig.height=6}
par(mfrow=c(2,2))
plot(dispWtVsCarb_model)
```

\pagebreak

```{r, fig.height=6}
ggpairs(mtcars)
```